Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-05 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:05	20:02:19	(Mon 5.Oct)

% 
% \begin{itemize}
% \item Dynamic weights $\Rightarrow$ greater contrast/resolution potential
% \item But:
% \begin{itemize}
% \item Active system $\Rightarrow$ noise and signal correlated $\Rightarrow$ adaptive beamformers no longer robust.
% \item Subarray averaging decorrelate the noise, but in the process we sacrifice resolution.
% \item Computationally complex O($M^3$) due to inversion of a spatial covariance matrix. LCA is only O($MW$). Even if Capon subspace/beamspace versions exist, they remain more complex than the LCA, and is not as ideally suited for implementation of SIMD hardware (GPUs, DSPs, ...).
% \end{itemize}
% \item LCA is inherently robust, is ``parameter free'' once setup with a well designed window set, and can often be implemented with minor modifications to already existing DAS beamformers.
% 
% The angular resolution and contrast in active sonar images depend on the beamformer's ability to receive signals from directions of interest, while suppressing noise and interference emanating from other directions. For sonar arrays, this is achieved by applying weights to the array channels.
% 
% While classical beamformers use predefined windows, adaptive beamformers estimate the optimal window by analytical evaluation of the data. The minimum variance (MV) beamformer, for instance, calculates the set of weights that minimises the variance of the beamformer's output. 
% 
We have implemented and studied the low complexity adaptive (LCA) beamformer in active sonar imaging. LCA is an attractive alternative to the minimum variance distortionless response (MVDR) method for minimizing noise and interference in sonar images. While MVDR estimates and inverts a spatial covariance matrix to achieve this goal, LCA iterates through a predefined set of sensor weights selecting the one that best fulfills the minimum variance criterion.

>>>>

% 
% \begin{itemize}
% \item Dynamic weights $\Rightarrow$ greater contrast/resolution potential
% \item But:
% \begin{itemize}
% \item Active system $\Rightarrow$ noise and signal correlated $\Rightarrow$ adaptive beamformers no longer robust.
% \item Subarray averaging decorrelate the noise, but in the process we sacrifice resolution.
% \item Computationally complex O($M^3$) due to inversion of a spatial covariance matrix. LCA is only O($MW$). Even if Capon subspace/beamspace versions exist, they remain more complex than the LCA, and is not as ideally suited for implementation of SIMD hardware (GPUs, DSPs, ...).
% \end{itemize}
% \item LCA is inherently robust, is ``parameter free'' once setup with a well designed window set, and can often be implemented with minor modifications to already existing DAS beamformers.
% 
% The angular resolution and contrast in active sonar images depend on the beamformer's ability to receive signals from directions of interest, while suppressing noise and interference emanating from other directions. For sonar arrays, this is achieved by applying weights to the array channels.
% 
% While classical beamformers use predefined windows, adaptive beamformers estimate the optimal window by analytical evaluation of the data. The minimum variance (MV) beamformer, for instance, calculates the set of weights that minimises the variance of the beamformer's output. 
% 
We have implemented and studied the low complexity adaptive (LCA) beamformer in active sonar imaging. LCA can be viewed as either a simplification of the minimum variance distortionless response (MVDR) beamformer, or as an adaptive extension to the delay and sum (DAS) beamformer. Both LCA and MVDR seek to minmimize noise and interference in the image, but while MVDR achieves this goal by estimating and inverting a spatial covariance matrix, LCA applies the optimal window iterates through a predefined set of sensor weights selecting the one that best fulfills the minimum variance criterion

 LCA is an attractive alternative to the  for minimizing noise and interference in sonar images. While MVDR estimates and inverts a spatial covariance matrix to achieve this goal, LCA iterates through a predefined set of sensor weights selecting the one that best fulfills the minimum variance criterion. using the same criterion as MVDR.
